Graph embedding and transfer learning can help predict potential species interaction networks despite data limitations

### 2023-08-15 index.qmd
done

The ability to infer *potential* interactions could serve as a significant breakthrough in our ability to conceptualize species interaction networks over large spatial scales [@Hortal2015Seven]. Reliable inferences would not only boost our understanding of the structure of species interaction networks, but also increase the amount of information that can be used for biodiversity management. In a recent overview of the field of ecological network prediction, @Strydom2021Roadmap identified two challenges of interest to the prediction of interactions at large scales. First, there is a relative scarcity of relevant data in most places globally -- which, due to the limitations in most predictive methods, restricts the ability to infer interactions to locations where it is least required (*i.e.* regions where we already have interaction data) leaving us unable to make inference in data scarce regions (where we most need it); second, accurate predictors are important for accurate predictions, and the lack of methods that can leverage a small amount of *accurate* data is a serious impediment to our predictive ability. In most places, our most reliable biodiversity knowledge is that of a species pool where a set of potentially interacting species in a given area could occur: through the analysis of databases like the Global Biodiversity Information Facility (GBIF) or the International Union for the Conservation of Nature (IUCN), it is possible to construct a list of species for a region of interest; however inferring the potential interactions between these species still remains a challenge.

Following the definition of @Dunne2006Network, a metaweb is the ecological network analogue to the species pool; specifically, it inventories all *potential* interactions between species for a spatially delimited area (and so captures the $\gamma$ diversity of interactions). The metaweb itself is not a prediction of local networks at specific locations within the spatial area it covers: it will have a different structure, notably by having a larger connectance [see *e.g.* @Wood2015Effects] and complexity [see *e.g.* @Galiana2022Ecological], than any of these local networks. These local networks (which capture the $\alpha$ diversity of interactions) are a subset of the metaweb's species and its realized interactions, and have been called "metaweb realizations" [@Poisot2015Species]. Differences between local networks and their metawebs are due to chance, species abundance and co-occurrence, local environmental conditions, and local distribution of functional traits, among others. Specifically, although co-occurrence can be driven by interactions [@Cazelles2016Theory], co-occurrence alone is not a predictor of interactions [@Blanchet2020Cooccurrence; @Thurman2019Testing], and therefore the lack of co-occurrence cannot be used to infer the lack of a feasible interaction. Yet, recent results by @Saravia2021Ecological strongly suggested that local (metaweb) realizations only respond weakly to local conditions: instead, they reflect constraints inherited by the structure of their metaweb. This sets up the core goal of predictive network ecology as the prediction of metaweb structure, as it is required to accurately produce downscaled, local predictions.

Because the metaweb represents the joint effect of functional, phylogenetic, and macroecological processes [@Morales-Castilla2015Inferring], it holds valuable ecological information. Specifically, it represents the "upper bounds" on what the composition of the local networks, given a local species pool, can be [see *e.g.* @McLeod2021Sampling]; this information can help evaluate the ability of ecological assemblages to withstand the effects of, for example, climate change [@Fricke2022Effects]. These local networks may be reconstructed given an appropriate knowledge of local species composition and provide information on the structure of food webs at finer spatial scales. This has been done for example for tree-galler-parasitoid systems [@Gravel2018Bringing], fish trophic interactions [@Albouy2019Marine], tetrapod trophic interactions [@Braga2019Spatial; @OConnor2020Unveiling], and crop-pest networks [@Grunig2020Crop]. In this contribution, we highlight the power of viewing (and constructing) metawebs as *probabilistic* objects in the context of low-probability interactions, discuss how a family of machine learning tools (graph embeddings and transfer learning) can be used to overcome data limitations to metaweb inference, and highlight how the use of metawebs introduces important questions for the field of network ecology.

@@

Yet, the original metaweb definition, and indeed most past uses of metawebs, was based on the presence/absence of interactions. Moving towards *probabilistic* metawebs, by representing interactions as Bernoulli events [see *e.g.* @Poisot2016Structure], offers the opportunity to weigh these rare interactions appropriately. The inherent plasticity of interactions is important to capture: there have been documented instances of food webs undergoing rapid collapse/recovery cycles over short periods of time [*e.g.* @Pedersen2017Signatures]. Furthermore, because the structure of the metaweb cannot be known in advance, it is important to rely on predictive tools that do not assume a specific network topology for link prediction [@Gaucher2021Outlier], but are able to work on generalizations of the network. These considerations emphasize why metaweb predictions should focus on quantitative (preferentially probabilistic) predictions, and this should constrain the suite of models that are appropriate for prediction.

It is important to recall that a metaweb is intended as a catalogue of all potential (feasible) interactions, which is then filtered for a given application [@Morales-Castilla2015Inferring]. It is therefore important to separate the interactions that happen "almost surely" (repeated observational data), "almost never" (repeated lack of evidence *or* evidence that the link is forbidden through *e.g.* trait mis-match), and interactions with a probability that lays somewhere in between [@Catchen2023Missing]. In a sense, that most ecological interactions are elusive can call for a slightly different approach to sampling: once the common interactions are documented, the effort required in documenting each rare interaction will increase exponentially [@Jordano2016Sampling]. Recent proposals in other fields relying on machine learning approaches emphasize the idea that algorithms meant to predict, through the assumption that they approximate the process generating the data, can also act as data generators [@Hoffmann2019Machine]. High quality observational data can be used to infer core rules underpinning network structure, and be supplemented with synthetic data coming from predictive models trained on them, thereby increasing the volume of information available for analysis. Indeed, @Strydom2021Roadmap suggested that knowing the metaweb may render the prediction of local networks easier, because it fixes an "upper bound" on which interactions can exist. In this context, a probabilistic metaweb represents an aggregation of informative priors on the biological feasibility of interactions, which is usually hard to obtain yet has possibly the most potential to boost our predictive ability of local networks [@Bartomeus2013Understanding; @Bartomeus2016Common]. This would represent a departure from simple rules expressed at the network scale [*e.g.* @Williams2000Simple] to a view of network prediction based on learning the rules that underpin interactions *and* their variability [@Gupta2022Simultaneously].

@@

Food webs are inherently low-dimensional objects, and can be adequately represented with less than ten dimensions [@Braga2021Phylogenetic; @Eklof2013Dimensionality; @Braga2019Spatial]. Simulation results by @Botella2022Appraisal suggested that there is no dominant method to identify architectural similarities between networks: multiple approaches need to be tested and compared to the network descriptor of interest on a problem-specific basis. This matches previous results on graph embedding, wherein different embedding algorithms yield different network embeddings [@Goyal2018Graph], calling for a careful selection of the problem-specific approach to use. In @tbl-methods, we present a selection of common graph and node embedding methods, alongside examples of their use to predict interactions or statistical associations between species. These methods rely largely on linear algebra or pseudo-random walks on graphs. All forms of embeddings presented in @tbl-methods share the common property of summarizing their objects into (sets of) dense feature vectors, that capture the overall network structure, pairwise information on nodes, and emergent aspects of the network, in a compressed way (*i.e.* with some information loss, as we later discuss in the illustration). Node embeddings tend to focus on maintaining pairwise relationships (*i.e.* species interactions), while graph embeddings focus on maintaining the network structure (*i.e.* emergent properties). Nevertheless, some graph embedding techniques [like RDPG, see *e.g.* @Wu2021Maximum] will provide high-quality node-level embeddings while also preserving network structure.

@@

| Method        | Object          | Technique                        | Reference                | Application                                                                                                       |
|-------------|-------------|-------------|-------------|--------------------|
| tSNE          | nodes           | statistical divergence           | @Hinton2002Stochastic    | [@Cieslak2020Tdistributed, species-environment responses $^a$] [@Gibb2021Data, host-virus network representation] |
| LINE          | nodes           | stochastic gradient descent      | @Tang2015Line            |                                                                                                                   |
| SDNE          | nodes           | gradient descent                 | @Wang2016Structural      |                                                                                                                   |
| node2vec      | nodes           | stochastic gradient descent      | @Grover2016Node2vec      |                                                                                                                   |
| HARP          | nodes           | meta-strategy                    | @Chen2017Harp            |                                                                                                                   |
| DMSE          | joint nodes     | deep neural network              | @Chen2017Deep            | [@Chen2017Deep, species-environment interactions $^b$]                                                            |
| graph2vec     | sub-graph       | skipgram network                 | @Narayanan2017Graph2vec  |                                                                                                                   |
| RDPG          | graph           | SVD                              | @Young2007Random         | [@DallaRiva2016Exploring, trophic interactions] [@Poisot2021Imputing, host-virus network prediction]              |
| GLEE          | graph           | Laplacian eigenmap               | @Torres2020Glee          |                                                                                                                   |
| DeepWalk      | graph           | stochastic gradient descent      | @Perozzi2014Deepwalk     | [@Wardeh2021Predicting, host-virus interactions]                                                                  |
| GraphKKE      | graph           | stochastic differential equation | @Melnyk2020Graphkke      | [@Melnyk2020Graphkke, microbiome species associations $^a$]                                                       |
| FastEmbed     | graph           | eigen decomposition              | @Ramasamy2015Compressive |                                                                                                                   |
| PCA           | graph           | eigen decomposition              | @Surendran2013Graph      | [@Strydom2021Roadmap, host-parasite interactions]                                                                 |
| Joint methods | multiple graphs | multiple strategies              | @Wang2021Joint           |                                                                                                                   |

@@

The popularity of graph embedding techniques in machine learning is more than the search for structural invariants: graphs are discrete objects, and machine learning techniques tend to handle continuous data better. Bringing a sparse graph into a continuous, dense vector space [@Xu2021Understanding] opens up a broader variety of predictive algorithms, notably of the sort that are able to predict events as probabilities [@Murphy2022Probabilistic]. Furthermore, the projection of the graph itself is a representation that can be learned; @Runghen2021Exploiting, for example, used a neural network to learn the embedding of a network in which not all interactions were known, based on the nodes' metadata. This example has many parallels in ecology (see @fig-embedding **C**), in which node metadata can be represented by phylogeny, abundance, or functional traits. Using phylogeny as a source of information assumes (or strives to capture) the action of evolutionary processes on network structure, which at least for food webs have been well documented [@Braga2021Phylogenetic; @DallaRiva2016Exploring; @Eklof2016Phylogenetic; @Stouffer2007Evidence; @Stouffer2012Evolutionary]; similarly, the use of functional traits assumes that interactions can be inferred from the knowledge of trait-matching rules, which is similarly well supported in the empirical literature [@Bartomeus2013Understanding; @Bartomeus2016Common; @Goebel2023Body; @Gravel2013Inferring]. Relating this information to an embedding rather than a list of network measures would allow to capture their effect on the more fundamental aspects of network structure; conversely, the absence of a phylogenetic or functional signal may suggest that evolutionary/trait processes are not strong drivers of network structure, therefore opening a new way to perform hypothesis testing.

@@

In @fig-illustration-1, we focus on some statistical checks of the embedding. In panel **A**, we show that the averaged $L_2$ loss (*i.e.* the mean of squared errors) between the empirical and reconstructed metaweb decreases when the number of dimensions (rank) of the subspace increases, with an inflection at 39 dimensions (out of 120 initially) according to the finite differences method. As discussed by @Runghen2021Exploiting, there is often a trade-off between the number of dimensions to use (more dimensions are more computationally demanding) and the quality of the representation. In panel **B**, we show the increase in cumulative variance explained at each rank, and visualize that using 39 ranks explains about 70% of the variance in the empirical metaweb. This is a different information from the $L_2$ loss (which is averaged across interactions), as it works on the eigenvalues of the embedding, and therefore captures higher-level features of the network. In panel **C**, we show positions of hosts and parasites on the first two dimensions of the left and right subspaces. Note that these values largely skew negative, because the first dimensions capture the coarse structure of the network: most pairs of species do not interact, and therefore have negative values. Finally in panel **D**, we show the predicted weight (*i.e.* the result of the multiplication of the RDGP subspaces at a rank of 39) as a function of whether the interactions are observed, not-observed, or unknown due to lack of co-occurrence in the original dataset. This reveals that the observed interactions have higher predicted weights, although there is some overlap; the usual approach to identify potential interactions based on this information would be a thresholding analysis, which is outside the scope of this manuscript (and is done in the papers cited in this illustration). Because the values returned from RDPG are not bound to the unit interval, we performed a clamping of the weights to the unit space, showing a one-inflation in documented interactions, and a zero-inflation in other species pairs. This last figure crosses from the statistical into the ecological, by showing that species pairs with no documented co-occurrence have weights that are not distinguishable from species pairs with no documented interactions, suggesting that (as befits a host-parasite model) the ability to interact is a strong predictor of co-occurrence.

@@

@@

>>>>

The ability to infer *potential* interactions could serve as a significant breakthrough in our ability to conceptualize species interaction networks over large spatial scales [@Hortal2015Seven]. Reliable inferences would not only boost our understanding of the structure of species interaction networks, but also increase the amount of information that can be used for biodiversity management. In a recent overview of the field of ecological network prediction, @Strydom2021Roadmap identified two challenges of interest to the prediction of interactions at large scales. First, there is a relative scarcity of relevant data in most places globally -- which, due to the limitations in most predictive methods, restricts the ability to infer interactions to locations where it is least required (*i.e.* regions where we already have interaction data) leaving us unable to make inference in data scarce regions (where we most need it); second, accurate predictors are important for accurate predictions, and the lack of methods that can leverage a small amount of *accurate* data is a serious impediment to our predictive ability. In this contribution, we highlight the power of viewing (and constructing) metawebs as *probabilistic* objects in the context of low-probability interactions, discuss how a family of machine learning tools (graph embeddings and transfer learning) can be used to overcome data limitations to metaweb inference, and highlight how the use of metawebs introduces important questions for the field of network ecology.

In most places, our most reliable biodiversity knowledge is that of a species pool where a set of potentially interacting species in a given area could occur: through the analysis of databases like the Global Biodiversity Information Facility (GBIF) or the International Union for the Conservation of Nature (IUCN), it is possible to construct a list of species for a region of interest. Following the definition of @Dunne2006Network, a metaweb is the ecological network analogue to the species pool; specifically, it inventories all *potential* interactions between species for a spatially delimited area (and so captures the $\gamma$ diversity of interactions as per @Poisot2012Dissimilarity). However, inferring the potential interactions between these species still remains a challenge. And yet, because the metaweb represents the joint effect of functional, phylogenetic, and macroecological processes [@Morales-Castilla2015Inferring; @carlson2022; @morales-castilla2021], it holds valuable ecological information. Specifically, it represents the "upper bounds" on what the composition of the local networks, given a local species pool, can be [see *e.g.* @McLeod2021Sampling]; this information can help evaluate the ability of ecological assemblages to withstand the effects of, for example, climate change [@Fricke2022Effects]. These local networks may be reconstructed given an appropriate knowledge of local species composition and provide information on the structure of networks at finer spatial scales. This has been done for example for tree-galler-parasitoid systems [@Gravel2018Bringing], fish trophic interactions [@Albouy2019Marine], tetrapod trophic interactions [@Braga2019Spatial; @OConnor2020Unveiling], and crop-pest networks [@Grunig2020Crop].

The metaweb itself is not a prediction of local networks at specific locations within the spatial area it covers: it will have a different structure, notably by having a larger connectance [see *e.g.* @Wood2015Effects] and complexity [see *e.g.* @Galiana2022Ecological], than any of these local networks. These local networks (which capture the $\alpha$ diversity of interactions) are a subset of the metaweb's species and its realized interactions, and have been called "metaweb realizations" [@Poisot2015Species]. Differences between local networks and their metawebs are due to chance, species abundance and co-occurrence, local environmental conditions, and local distribution of functional traits, among others. Specifically, although co-occurrence can be driven by interactions [@Cazelles2016Theory], co-occurrence alone is not a predictor of interactions [@Blanchet2020Cooccurrence; @Thurman2019Testing], and therefore the lack of co-occurrence cannot be used to infer the lack of a feasible interaction. Yet, recent results by @Saravia2021Ecological strongly suggested that local (metaweb) realizations only respond weakly to local conditions: instead, they reflect constraints inherited by the structure of their metaweb. This sets up the core goal of predictive network ecology as the prediction of metaweb structure, as it is required to accurately produce downscaled, local predictions.

@@

Yet, the original metaweb definition, and indeed most past uses of metawebs, was based on the presence/absence of interactions. Moving towards *probabilistic* metawebs, by representing interactions as Bernoulli events [see *e.g.* @Poisot2016Structure], offers the opportunity to weigh these rare interactions appropriately. The inherent plasticity of interactions is important to capture: there have been documented instances of food webs undergoing rapid collapse/recovery cycles over short periods of time [*e.g.* @Pedersen2017Signatures]. Furthermore, because the structure of the metaweb cannot be known in advance, it is important to rely on predictive tools that do not assume a specific network topology for link prediction [@Gaucher2021Outlier], but are able to work on generalizations of the network. These considerations emphasize why metaweb predictions should focus on quantitative (preferentially probabilistic) predictions, and this should constrain the suite of models that are appropriate for prediction. Binary classifiers based on probabilities have an extremely robust methodology to validate them, and this applies naturally to the prediction of interactions [@poisot2023].

It is important to recall that a metaweb is intended as a catalogue of all potential (feasible) interactions, which is then filtered for a given application [@Morales-Castilla2015Inferring]. It is therefore important to separate the interactions that happen "almost surely" (repeated observational data), "almost never" (repeated lack of evidence *or* evidence that the link is forbidden through *e.g.* trait mis-match), and interactions with a probability that lays somewhere in between [@Catchen2023Missing]. Although metawebs can (and in practice likely do) include false positives, these are statistically negligible compared to the false negatives. Furthermore, @Strydom2022Food shows that t-SVD embedding is extremely robust to (and able to detect) the presence of false positives. In a sense, that most ecological interactions are elusive can call for a slightly different approach to sampling: once the common interactions are documented, the effort required in documenting each rare interaction will increase exponentially [@Jordano2016Sampling]. Recent proposals in other fields relying on machine learning approaches emphasize the idea that algorithms meant to predict, through the assumption that they approximate the process generating the data, can also act as data generators [@Hoffmann2019Machine]. High quality observational data can be used to infer core rules underpinning network structure, and be supplemented with synthetic data coming from predictive models trained on them, thereby increasing the volume of information available for analysis. Indeed, @Strydom2021Roadmap suggested that knowing the metaweb may render the prediction of local networks easier, because it fixes an "upper bound" on which interactions can exist. In this context, a probabilistic metaweb represents an aggregation of informative priors on the biological feasibility of interactions, which is usually hard to obtain yet has possibly the most potential to boost our predictive ability of local networks [@Bartomeus2013Understanding; @Bartomeus2016Common]. This would represent a departure from simple rules expressed at the network scale [*e.g.* @Williams2000Simple] to a view of network prediction based on learning the rules that underpin interactions *and* their variability [@Gupta2022Simultaneously].

@@

Ecological networks are inherently low-dimensional objects, and can be adequately represented with less than ten dimensions [@Braga2021Phylogenetic; @Eklof2013Dimensionality; @Braga2019Spatial]. Simulation results by @Botella2022Appraisal suggested that there is no dominant method to identify architectural similarities between networks: multiple approaches need to be tested and compared to the network descriptor of interest on a problem-specific basis. This matches previous results on graph embedding, wherein different embedding algorithms yield different network embeddings [@Goyal2018Graph], calling for a careful selection of the problem-specific approach to use. Additionally, @ghasemian2020 suggest that in some cases, nodes embeddings can be outperformed by other methods, re-inforcing the need to thoroughly select the appropriate data analysis technique. In @tbl-methods, we present a selection of common graph and node embedding methods, alongside examples of their use to predict interactions or statistical associations between species. These methods rely largely on linear algebra or pseudo-random walks on graphs. All forms of embeddings presented in @tbl-methods share the common property of summarizing their objects into (sets of) dense feature vectors, that capture the overall network structure, pairwise information on nodes, and emergent aspects of the network, in a compressed way (*i.e.* with some information loss, as we later discuss in the illustration). Node embeddings tend to focus on maintaining pairwise relationships (*i.e.* species interactions), while graph embeddings focus on maintaining the network structure (*i.e.* emergent properties). Nevertheless, some graph embedding techniques [like RDPG, see *e.g.* @Wu2021Maximum] will provide high-quality node-level embeddings while also preserving network structure.

@@

| Method        | Object          | Technique                        | Reference                | Application                                                                                                       |
|---------------|---------------|---------------|---------------|---------------|
| tSNE          | nodes           | statistical divergence           | @Hinton2002Stochastic    | [@Cieslak2020Tdistributed, species-environment responses $^a$] [@Gibb2021Data, host-virus network representation] |
| LINE          | nodes           | stochastic gradient descent      | @Tang2015Line            |                                                                                                                   |
| SDNE          | nodes           | gradient descent                 | @Wang2016Structural      |                                                                                                                   |
| node2vec      | nodes           | stochastic gradient descent      | @Grover2016Node2vec      |                                                                                                                   |
| HARP          | nodes           | meta-strategy                    | @Chen2017Harp            |                                                                                                                   |
| DMSE          | joint nodes     | deep neural network              | @Chen2017Deep            | [@Chen2017Deep, species-environment interactions $^b$]                                                            |
| graph2vec     | sub-graph       | skipgram network                 | @Narayanan2017Graph2vec  |                                                                                                                   |
| RDPG          | graph           | SVD                              | @Young2007Random         | [@DallaRiva2016Exploring, trophic interactions] [@Poisot2021Imputing, host-virus network prediction]              |
| GLEE          | graph           | Laplacian eigenmap               | @Torres2020Glee          |                                                                                                                   |
| DeepWalk      | graph           | stochastic gradient descent      | @Perozzi2014Deepwalk     | [@Wardeh2021Predicting, host-virus interactions]                                                                  |
| GraphKKE      | graph           | stochastic differential equation | @Melnyk2020Graphkke      | [@Melnyk2020Graphkke, microbiome species associations $^a$]                                                       |
| FastEmbed     | graph           | eigen decomposition              | @Ramasamy2015Compressive |                                                                                                                   |
| PCA           | graph           | eigen decomposition              | @Surendran2013Graph      | [@Strydom2021Roadmap, host-parasite interactions]                                                                 |
| Joint methods | multiple graphs | multiple strategies              | @Wang2021Joint           |                                                                                                                   |

@@

The popularity of graph embedding techniques in machine learning is more than the search for structural invariants: graphs are discrete objects, and machine learning techniques tend to handle continuous data better. Bringing a sparse graph into a continuous, dense vector space [@Xu2021Understanding] opens up a broader variety of predictive algorithms, notably of the sort that are able to predict events as probabilities [@Murphy2022Probabilistic]. Furthermore, the projection of the graph itself is a representation that can be learned; @Runghen2021Exploiting, for example, used a neural network to learn the embedding of a network in which not all interactions were known, based on the nodes' metadata. This example has many parallels in ecology (see @fig-embedding **C**), in which node metadata can be represented by phylogeny, abundance, or functional traits. Using phylogeny as a source of information assumes (or strives to capture) the action of evolutionary processes on network structure, which at least for networks have been well documented [@Braga2021Phylogenetic; @DallaRiva2016Exploring; @Eklof2016Phylogenetic; @Stouffer2007Evidence; @Stouffer2012Evolutionary]; similarly, the use of functional traits assumes that interactions can be inferred from the knowledge of trait-matching rules, which is similarly well supported in the empirical literature [@Bartomeus2013Understanding; @Bartomeus2016Common; @Goebel2023Body; @Gravel2013Inferring]. Relating this information to an embedding rather than a list of network measures would allow to capture their effect on the more fundamental aspects of network structure; conversely, the absence of a phylogenetic or functional signal may suggest that evolutionary/trait processes are not strong drivers of network structure, therefore opening a new way to perform hypothesis testing.

@@

In @fig-illustration-1, we focus on some statistical checks of the embedding. In panel **A**, we show that the averaged $L_2$ loss (*i.e.* the mean of squared errors) between the empirical and reconstructed metaweb decreases when the number of dimensions (rank) of the subspace increases, with an inflection at 39 dimensions (out of 120 initially) according to the finite differences method. As discussed by @Runghen2021Exploiting, there is often a trade-off between the number of dimensions to use (more dimensions are more computationally demanding) and the quality of the representation. In panel **B**, we show the increase in cumulative variance explained at each rank, and visualize that using 39 ranks explains about 70% of the variance in the empirical metaweb. This is a different information from the $L_2$ loss (which is averaged across interactions), as it works on the eigenvalues of the embedding, and therefore captures higher-level features of the network. In panel **C**, we show positions of hosts and parasites on the first two dimensions of the left and right subspaces. Note that these values largely skew negative, because the first dimensions capture the coarse structure of the network: most pairs of species do not interact, and therefore have negative values. Finally in panel **D**, we show the predicted weight (*i.e.* the result of the multiplication of the RDGP subspaces at a rank of 39) as a function of whether the interactions are observed, not-observed, or unknown due to lack of co-occurrence in the original dataset. This reveals that the observed interactions have higher predicted weights, although there is some overlap; the usual approach to identify potential interactions based on this information would be a thresholding analysis, which is outside the scope of this manuscript (and is done in the papers cited in this illustration). Because the values returned from RDPG are not bound to the unit interval, we performed a clamping of the weights to the unit space, showing a one-inflation in documented interactions, and a zero-inflation in other species pairs. This last figure shows that species pairs with no documented co-occurrence have weights that are not distinguishable from species pairs with no documented interactions; in other words, looking at the embedding, species that do not co-occur are not easily distinguished from species that do not interact. This suggests that (as befits a host-parasite model) the ability to interact is a strong predictor of co-occurrence.

@@

## Putting models in their context

@@

Although promising, the application of embeddings to metaweb prediction will require to address several challenges. First, there is a need to understand how to define a metaweb as a single, cohesive, unit of ecological organisation. This is likely to admit very different answers based on the specific taxonomic group, temporal and spatial resolution, and question being investigated. Second, there is a need to understand the scale at which these predictions are relevant. Although we have documented many cases of using embedding to fill gaps in the metaweb, these techniques can likely be brought into a spatial (and possibly temporal) context. The validation of these predictions will have to proceed jointly with empirical sampling of interactions, but also with the design of downsampling methods. Finally, there is a need for a greater understanding of how biases in the data propagate to the predictions. Because the volume of metawebs is currently low, and because graph embeddings have not been commonly applied, we anticipate that this discussion will take place organically in the coming years.
